### 2022-11-01 mycv/subs/papers.tex
updates

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
  \cventry
  {B. Jeon, M.-S. Kim, S. Choi, \underline{Y. Jeong}$^*$}
  {\href{}{Finite element analysis using elasto-visco-plastic self-consistent polycrystal model for E-form Mg sheet subjected to bending}}
  {Journal of Magnesium and Alloys}
  {Accepted}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {M. Joo, M.-S. Wi, S.-Y. Yoon, S.-Y. Lee, F. Barlat, C N. Tom\'{e}, B. Jeon, \underline{Y. Jeong}$^*$}
  {\href{https://doi.org/10.1016/j.ijmecsci.2022.107796}{A crystal plasticity finite element analysis on the effect of prestrain on springback   }}
  {In press}
  {}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {J. Park, \underline{Y. Jeong}$^*$}
  {\href{http://dx.doi.org/10.3365/KJMM.2022.60.8.607}{Prediction and validation of stress triaxiality assisted by elasto-visco-plastic polycrystal model}}
  {Korean Journal of Metals and Materials}
  {Vol. 60 (8), 607-618, 2022}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {M.S. Lee, T. Kawasaki, T. Yamashita, S. Harjo, Y.T. Hyun, \underline{Y. Jeong}, T. S. Jun$^*$}
  {\href{https://doi.org/10.1038/s41598-022-07640-3}{In-situ neutron diffraction study of lattice deformation behaviour of commercially pure titanium at cryogenic temperature}}
  {Scientific Reports}
  {Vol. 12 (1), 1-10, 2022}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, B. Jeon, C N. Tom\'{e}}
  {\href{https://doi.org/10.1016/j.ijplas.2021.103110}{Finite element analysis using an incremental elasto-visco-plastic self-consistent polycrystal model: FE simulations on Zr and low-carbon steel subjected to bending, stress-relaxation, and unloading}}
  {International Journal of Plasticity}
  {Vol. 147, 103110, 2021}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
  {\href{https://doi.org/10.1016/j.ijplas.2020.102812}{An efficient elasto-visco-plastic self-consistent formulation: Application to steel subjected to loading path changes}}
  {International Journal of Plasticity}
  {Vol. 135, 102812, 2020}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, D. Steglich}
  {\href{https://doi.org/10.1016/j.ijmecsci.2020.105680}{Modelling-assisted description of anisotropic edge failure in magnesium sheet alloy under mixed-mode loading}}
  {International Journal of Mechanical Sciences}
  {Vol. 181, 105680, 2020}
  {
  }

>>>>

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
  \cventry
  {B. Jeon, M.-S. Kim, S. Choi, \underline{Y. Jeong}$^*$}
  {\href{}{Finite element analysis using elasto-visco-plastic self-consistent polycrystal model for E-form Mg sheet subjected to bending}}
  {Journal of Magnesium and Alloys}
  {Accepted}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {M. Joo, M.-S. Wi, S.-Y. Yoon, S.-Y. Lee, F. Barlat, C N. Tom\'{e}, B. Jeon, \underline{Y. Jeong}$^*$}
  {\href{https://doi.org/10.1016/j.ijmecsci.2022.107796}{A crystal plasticity finite element analysis on the effect of prestrain on springback}}
  {International Journal of Mechanical Sciences}
  {In press}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {Lalit Kauschik, Ki-Seong Park, Jeong-Gyun Kim, Jae-Seong Lee, Youngung Jeong, Shi-Hoon Choi$^*$}
  {\href{https://doi.org/10.1016/j.ijplas.2022.103467}{Reconstructing orientation data from the images of IPF maps and ODF sections extracted from the literature: A data-collection method for machine learning}}
  {International Journal of Plasticity}
  {Vol. 159, 103467, 2022}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {J. Park, \underline{Y. Jeong}$^*$}
  {\href{http://dx.doi.org/10.3365/KJMM.2022.60.8.607}{Prediction and validation of stress triaxiality assisted by elasto-visco-plastic polycrystal model}}
  {Korean Journal of Metals and Materials}
  {Vol. 60 (8), 607-618, 2022}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {M.S. Lee, T. Kawasaki, T. Yamashita, S. Harjo, Y.T. Hyun, \underline{Y. Jeong}, T. S. Jun$^*$}
  {\href{https://doi.org/10.1038/s41598-022-07640-3}{In-situ neutron diffraction study of lattice deformation behaviour of commercially pure titanium at cryogenic temperature}}
  {Scientific Reports}
  {Vol. 12 (1), 1-10, 2022}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, B. Jeon, C N. Tom\'{e}}
  {\href{https://doi.org/10.1016/j.ijplas.2021.103110}{Finite element analysis using an incremental elasto-visco-plastic self-consistent polycrystal model: FE simulations on Zr and low-carbon steel subjected to bending, stress-relaxation, and unloading}}
  {International Journal of Plasticity}
  {Vol. 147, 103110, 2021}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
  {\href{https://doi.org/10.1016/j.ijplas.2020.102812}{An efficient elasto-visco-plastic self-consistent formulation: Application to steel subjected to loading path changes}}
  {International Journal of Plasticity}
  {Vol. 135, 102812, 2020}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, D. Steglich}
  {\href{https://doi.org/10.1016/j.ijmecsci.2020.105680}{Modelling-assisted description of anisotropic edge failure in magnesium sheet alloy under mixed-mode loading}}
  {International Journal of Mechanical Sciences}
  {Vol. 181, 105680, 2020}
  {
  }
